Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-04-27 Ben_Manuscripts/structure_paper/Outline.tex
Outline updates

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  We used experimental wide angle X-ray scattering (WAXS) data (produced as described
  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
  to inform our choices of some initial structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily
  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
  \begin{itemize}
        \item There are five major features of interest present in the 2D experimental
        pattern shown in Figure~\ref{fig:WAXS}.
        \item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
        reflection will be referred to as R-$\pi$.
        \item A weak intensity line is located at exactly half the $q_z$ value of
        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
        real space periodic spacing of 7.4 \angstrom~. This reflection has been
        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
        along the z axis meaning if the positions of the aromatic rings can
        be traced by a helix, then for each turn in the helix, there should be
        two aromatic rings. For this reason it will be referred to as R-helix.
        \item A third major reflection is marked by a low intensity ring located
        at r = 1.4 \angstrom$^-1$. The real space separation
        corresponds to 4.5 \angstrom~ which is characteristic of the average
        spacing between packed alkane chains. This reflection will be called R-alkanes.
        \item Within R-alkanes, are four spots of higher relative intensity which
        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
        in their respective quadrants. In many liquid crystal systems this can be
        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: References
        \item The final feature corresponds to the spacing and symmetry of
        the d\textsubscript{100} plane which can be related to the distance between
        pores. The feature, which will be called R-pores, is characterized by dots
        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
        symmetry of the packed pores. The same information at higher resolution is obtained using a SAXS
        setup. By radially integrating the 2D data one gets a 1D curve which is
        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
  \end{itemize}

@@

  %BJC3: Feel free to suggest different words
  \subsection{Density of monomers around pores}
  %MRS4: Perhaps instead of talking about ``layers'', we can talk about axial density correlations.  You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.  
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
  		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
  		procedure.
  		\item The pore-to-pore spacing is stable in all systems are stable after 400 ns of 
  		simulation. Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all 
  		systems tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
  \end{itemize}

@@

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of monomers in each layer increases. The pore spacing
			 of systems starting in the sandwiched configuration are systematically lower
			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
  \end{figure}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. 
  \begin{itemize}
	  	\item We tested systems built with 5 monomers per layer in the parallel 
		displaced and sandwiched configurations at 300K.
		\item We generated simulated patterns using portions of simulation trajectory
		after equilibration.
		\item The patterns for both structures are shown and compared to experiment
		in Figure~\ref{fig:XRDsim}.
  \end{itemize}

%  Simulated XRD of the sandwiched configuration contains all experimental
%  features except for R-helix. R-alkanes, R-spots and R-pores appear close to their
%  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
%  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
%  to stack farther apart.

%  Like the sandwiched configuration, the parallel displaced configuration creates
%  a simulated XRD pattern with all major experimental reflections except for R-helix.
%  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
%  and R-$\pi$ appear, however with a lower intensity
%  relative to R-alkanes when compared to the sandwiched configuration. R-helix
%  appears due to the parallel displaced aromatic rings. It is a subharmonic of
%  R-$\pi$ since the nearest vertically stacked head group to any given head group
%  is $2\times$R-$\pi$~away. 
% BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib

% BJC3: update with 300K pics. Presented separately from 280K for now. 
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_offset_300K.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.285]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_layered_300K.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-4.00em}
        \includegraphics[width=\linewidth]{colorbar_seismic.png}
  \end{subfigure}
%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced. Any thoughts why? We can discuss in person.  And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
%BJC2: Sure, I'll add that to supporting info
  \caption{The simulated XRD pattern generated from the equilibrated trajectory
	  of the parallel displaced configuration (a) exhibits all major reflections
	  present in the experimental WAXS pattern (b). The simulated XRD pattern
	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
	  all major reflections except R-helix.}
  \label{fig:XRDsim}
  \end{figure}

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
    %MRS4: we will need to provide more details: more intense is just qualiatative.
  		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
    %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
	  \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
	    reflection reaches its maximum at c.a. $q_z=1.4$ which means that monomers prefer 
	    to stack c.a. 4.5 \AA apart rather than 3.7 \AA. This behavior is not surprising since
	    GAFF models atoms as point charges and does not appropriately model the aromatic
	    $\pi-\pi$ interactions which would cause the monomers to stack closer together.
	    \item R-spots is missing in both places, at least visually. The tails in our model
	    are more disordered than the experimental system at 300K.  
            %MRS4: are they really missing?  If Fig 7 is 300K, sandwiched seems to have it, and parallel displaced is hard to tell because it's covered by the main pi-pi-stacking
            %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
	    \item R-helix does not appear in either case.
            %MRS4: is r-helix a good name, when a helix would appear on either side of the center, not the center itself?
  \end{itemize}

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. 
  \begin{itemize}
  		\item There are horizontal reflections at $|q_z|= 0.7 \AA^{-1}$, exactly half of 
  		the $q_z$ value of R-$\pi$. 
  		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
  		appear for the same reason as R-helix. 
  		\item It is possible that these reflections contribute to the continuation of
  		R-helix into R-alkanes, as seen in the experimental pattern. 
  \end{itemize}

  There are numerical discrepancies between the relative intensities of each reflection when
  comparing experimental and simulated patterns.
  \begin{itemize}
  		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
  		of each reflection.
  		\item The intensity of R-spots is much lower than experiment (need to update the numbers in that table with 300K results)
  		\item There is no R-helix intensity
  		\item R-$\pi$ is nearly an order of magnitude higher in our simulations
  		compared to experiment.
  \end{itemize}

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  		   & \multicolumn{3}{c}{Configuration} \\
  \hline
  Reflection & Experiment & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0  \\  
  R-$\pi$   & 2.8 & 18.0 & 14.0  \\
  R-spots   & 1.5 &  1.6 &  1.2  \\  % Need to get these actual data points
  R-helix   & 0.9 &  --  & --    \\ 
  \bottomrule
  \end{tabular}
  \caption{The relative intensities of reflections of interest}
  \label{table:relative_inensities_300K} 
  \end{table}

%  The simulated XRD pattern produced from the sandwiched configuration is missing
%  R-helix and R-spots. 
%  \begin{itemize}
%		\item R-pores and R-alkanes appear in their expected locations. 
%		\item R-pores is more intense than experiment, likely because we are simulating a 
%		perfect, infinite hexagonal array. The real system has defects and domain misalignment
%	    which decreases the overall intensity.
%	    \item R-$\pi$ appears with a very high intensity and is shifted down to a lower value
%	    of $q_z$ meaning monomers in our model prefer to stack farther apart.  
%	    \item R-spots may be faintly present, however it is not present to the degree shown
%	    experimentally. (see table with relative intensities) 
%  \end{itemize}

  %BJC: discussed parallel displaced and sandwiched configs in separate paragraphs to 
  % avoid confusion. Need to make thesis less dry. 
%  The simulated XRD pattern generated from the parallel displaced configuration is also
%  missing R-helix and R-spots.
%  \begin{itemize}
%  		\item R-pores and R-alkanes appear in the expected location again
%  		\item R-$\pi$ is present in the same location as the sandwiched configuration with
%  		high intensity. 
%  		\item R-helix is not present, however off-axis reflections appear at the same value 
%  		of $q_z$ where we expect to see R-helix. These appear since there is a helical 
%  		arrangement of monomers in the parallel displaced configuration. A helix alone will
%  		not give rise to a reflection at $q_r = 0$ (See supporting info for demonstration)
%  		\item There is elevated intensity where we expect to see R-spots, however it cannot
%  		be easily distinguished from the higher intensity arcs which overlay the top and 
%  		bottom of R-alkanes.
%  \end{itemize}

%  The simulated diffraction patterns indicate that there is something going wrong
%  with the way the system is modeled. We must address all of these issues and justify
%  their occurrence.
  There are clear differences between our simulated results and experimental results
  that must be addressed and justified. We will explore the origin of each experimental 
  reflection and hypothesize why they do not appear in our simulated patterns. Specifically,
  we want answer:  
  %BJC: I could number these and answer them individually
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-helix?
  \end{enumerate}

  \subsubsection{Origin of R-spots}

  We observed R-spots when we ran simulations of each system at 280K. (figure to be added - include with 300K patterns or keep separate??)
  \begin{itemize}
  		\item R-spots is most intense in the sandwiched configuration
  		\item Still no R-helix
  \end{itemize}

  %BJC: might be able to combine with other table
  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  		   & \multicolumn{3}{c}{Configuration} \\
  \hline
  Reflection & Experiment & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0  \\  
  R-$\pi$   & 2.8 & 27.0 & 119.0  \\
  R-spots   & 1.5 &  1.6 &  1.2  \\  
  R-helix   & 0.9 &  --  & --    \\ 
  \bottomrule
  \end{tabular}
  \caption{The relative intensities of reflections of interest}
  \label{table:relative_inensities_300K} 
  \end{table}

  %BJC3: following taken from draft.tex
  The R-spots signal, which appears in both simulated XRD patterns, is not a
  result of alkane chain tilt. Previous literature has attributed the spots in
  this particular WAXS pattern as the product of tilted alkane
  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
  configuration since R-spots appears with the most strength in its simulated XRD
  pattern. We measured the tilt angle of the alkane chains and showed that our
  system equilibrates to an average tilt angle close to zero degrees
  (Fig.~\ref{fig:tilt}).

  %BJC3: from draft.tex  
  To understand the origin of R-spots, we determined which
  atoms gave rise to the feature. Since R-spots is present as higher intensity
  spots within R-alkanes, it is likely that the spots arise as a consequence of
  the tails. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern, we were able to isolate the cause of the spots to the
  tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
  the centroids of the tails and measured the angle between each centroid and its
  nearest neighbors with respect to the plane of the membrane.  We see distinct
  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle is near 7\degree~which is far from the
	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
  %BJC2: good idea
  \end{figure}

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
  location where the highest intensity of spots are located on the simulated
  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
  performed the same integration on the raw experimental data and found the angle
  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
  is a reconcilable difference with our simulated results.

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  We used experimental wide angle X-ray scattering (WAXS) data (produced as described
  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
  to inform our choices of some initial structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily
  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
  \begin{itemize}
        \item There are five major features of interest present in the 2D experimental
        pattern shown in Figure~\ref{fig:WAXS}.
        \item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
        reflection will be referred to as R-$\pi$.
        \item A weak intensity line is located at exactly half the $q_z$ value of
        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
        real space periodic spacing of 7.4 \angstrom~. This reflection has been
        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
        along the z axis meaning if the positions of the aromatic rings can
        be traced by a helix, then for each turn in the helix, there should be
        two aromatic rings. For this reason it will be referred to as R-double.
        \item A third major reflection is marked by a low intensity ring located
        at r = 1.4 \angstrom$^-1$. The real space separation
        corresponds to 4.5 \angstrom~ which is characteristic of the average
        spacing between packed alkane chains. This reflection will be called R-alkanes.
        \item Within R-alkanes, are four spots of higher relative intensity which
        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
        in their respective quadrants. In many liquid crystal systems this can be
        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: References
        \item The final feature corresponds to the spacing and symmetry of
        the d\textsubscript{100} plane which can be related to the distance between
        pores. The feature, which will be called R-pores, is characterized by dots
        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
        symmetry of the packed pores. The same information at higher resolution is obtained using a SAXS
        setup. By radially integrating the 2D data one gets a 1D curve which is
        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
  \end{itemize}

@@

  %BJC3: Feel free to suggest different words
  \subsection{Density of monomers around pores}
  %MRS4: Perhaps instead of talking about ``layers'', we can talk about axial density correlations.  You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.  
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
  		\item We built systems in both the parallel displaced and sandwiched configurations and
  		equilibrated them according to the dry equilibration procedure.
  		\item We test all systems with an initial layer spacing, l, of 3.7 \AA.
  		\item We tested 4 additional systems with layers initially spaced 5 \AA~apart (See 
  		supporting info for more details on sensitivity to initial layer spacing)
  		\item The pore-to-pore spacing is stable in all systems after 400 ns of simulation. 
  		Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems 
  		tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
	    \item comment about disordered systems
  \end{itemize}

@@

  % BJC4: I will add 6 mon/layer disordered data once I have it.
  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm, regardless of initial layer spacing, l. The 
			 equilibrated pore spacing of the model increases as the number of monomers 
			 in each layer increases. The pore spacing of systems starting in the sandwiched 	
			 configuration are systematically lower than those started in the parallel 
			 displaced configuration.}~\label{fig:p2p}
  \end{figure}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. 
  \begin{itemize}
	  	\item We tested systems built with 5 monomers per layer in the parallel 
		displaced and sandwiched configurations at 300 K with layers initially spaced
		3.7 \AA and 5.0 \AA apart.
		\item We generated simulated patterns using portions of simulation trajectory
		after equilibration.
		\item The patterns for all structures are shown and compared to experiment
		in Figure~\ref{fig:XRDsim}.
  \end{itemize}

%  Simulated XRD of the sandwiched configuration contains all experimental
%  features except for R-double. R-alkanes, R-spots and R-pores appear close to their
%  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
%  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
%  to stack farther apart.

%  Like the sandwiched configuration, the parallel displaced configuration creates
%  a simulated XRD pattern with all major experimental reflections except for R-double.
%  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
%  and R-$\pi$ appear, however with a lower intensity
%  relative to R-alkanes when compared to the sandwiched configuration. R-double
%  appears due to the parallel displaced aromatic rings. It is a subharmonic of
%  R-$\pi$ since the nearest vertically stacked head group to any given head group
%  is $2\times$R-$\pi$~away. 
% BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib

%BJC4: I'm not sure what the best way to set up this figure is yet.
  \begin{figure}[htb]
	\centering
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
	        		\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet.png}
			        \caption{Sanwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}

			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet.png}
	        		\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet.png}
			        \caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
			\end{subfigure}

			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet.png}
			        \caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
			\end{subfigure}
	\end{subfigure}
	\caption{Very descriptive caption}~\label{fig:XRDsim} 
	\end{figure}

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
    %MRS4: we will need to provide more details: more intense is just qualiatative.
    %BJC4: I can include the intensity of the first peak of R-pores in the tables that 
    % show relative intensities.
  		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
    %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
    %BJC4: So a combo of: domain misalignment, slow dynamics of simulated system, only 4 pores
    % in unit cell, tortuosity (?)
    	\item R-spots appears to be weaker in the simulated patterns. They are also partially 
	    engulfed by the wide R-$\pi$ reflection.
	    \item We further explore R-spots in Section~\ref{section:rspots}  
        \item R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the
	    reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers
	    prefer stack greater than 4.2 \AA apart rather than 3.7 \AA. This behavior is not
	    surprising since GAFF models atoms as point charges and does not appropriately model 
	    the aromatic $\pi-\pi$ interactions which would cause the monomers to stack closer
	    together.
	    \item We will explore R-$\pi$ in more detail in Section~\ref{section:rpi}.
            %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
			%BJC: Might have something to do with the distibution of tilt angles in the tails
	    \item R-double does not appear in any of the patterns
	    \item We will explore its possible origins and reasons that it does not appear in our
	    simulated patterns in Section~\ref{section:rdouble}.
  \end{itemize}

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. 
  \begin{itemize}
  		\item There are horizontal reflections at $|q_z|= 0.7 \AA^{-1}$, exactly half of 
  		the $q_z$ value of R-$\pi$. 
  		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
  		appear for the same reason as R-double. 
  		\item This type of pattern is characteristic of a helix (reference something)
  		\item It is possible that these reflections contribute to the continuation of
  		R-double into R-alkanes, as seen in the experimental pattern. 
  \end{itemize}

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  \begin{itemize}
  		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
  		of each reflection for each system tested.
  		\item The patterns are normalized so that the average intensity of R-alkanes equals 1. 
  		% BJC4: I need to explain how I calculated these intensities somewhere. Is this the right
  		% place to do it? I think it would just be confusing in the methods. I could also move it
  		% to supplemental.
  		\item We measured the approximate intensity of R-$\pi$ by measuring the intensity of 
  		the peak of the cross-section at $q_r=0$. 
  		\item The relative intensity of R-$\pi$ is significantly higher than experiment in our
  		simulations.
  		\item R-spots is measured as the average intensity within the region bounded by a 'spot'.
  		Spots are identified based on visual inspection. If there is no easily discernable spot,
  		then the intensity is taken as that of the intersection of R-alkanes at half the $q_z$
  		value of R-$\pi$, since that is where it appears experimentally. 
  		\item The intensity of R-spots is slightly lower than experiment in all cases.
  		\item There is no R-double intensity to be measured.
  \end{itemize}

  \begin{table}[h]
  \centering
  \begin{tabular}{cccccc}
  \toprule
  		   & \multicolumn{5}{c}{Configuration} \\
  \hline
  Reflection & Experiment & Sandwiched & Parallel Displaced & Disordered Sandwiched & Disordered Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

%  The simulated XRD pattern produced from the sandwiched configuration is missing
%  R-double and R-spots. 
%  \begin{itemize}
%		\item R-pores and R-alkanes appear in their expected locations. 
%		\item R-pores is more intense than experiment, likely because we are simulating a 
%		perfect, infinite hexagonal array. The real system has defects and domain misalignment
%	    which decreases the overall intensity.
%	    \item R-$\pi$ appears with a very high intensity and is shifted down to a lower value
%	    of $q_z$ meaning monomers in our model prefer to stack farther apart.  
%	    \item R-spots may be faintly present, however it is not present to the degree shown
%	    experimentally. (see table with relative intensities) 
%  \end{itemize}

  %BJC: discussed parallel displaced and sandwiched configs in separate paragraphs to 
  % avoid confusion. Need to make thesis less dry. 
%  The simulated XRD pattern generated from the parallel displaced configuration is also
%  missing R-double and R-spots.
%  \begin{itemize}
%  		\item R-pores and R-alkanes appear in the expected location again
%  		\item R-$\pi$ is present in the same location as the sandwiched configuration with
%  		high intensity. 
%  		\item R-double is not present, however off-axis reflections appear at the same value 
%  		of $q_z$ where we expect to see R-double. These appear since there is a helical 
%  		arrangement of monomers in the parallel displaced configuration. A helix alone will
%  		not give rise to a reflection at $q_r = 0$ (See supporting info for demonstration)
%  		\item There is elevated intensity where we expect to see R-spots, however it cannot
%  		be easily distinguished from the higher intensity arcs which overlay the top and 
%  		bottom of R-alkanes.
%  \end{itemize}

  There are clear differences between our simulated results and experimental results
  that must be addressed and justified. We will explore the origin of each experimental 
  reflection and form structural hypotheses related to their appearance in our simulated 
  patterns. Specifically, we want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

  \subsubsection{Origin of R-spots}\label{section:rspots}

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. 
  \begin{itemize}
  		\item R-spots is most intense in the sandwiched configuration
  		(Figure~\ref{fig:sandwiched280K}).
  		\item The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3) 
  		\item Still no R-double
  		\item We can use this configuration to more thoroughly explore the origin of R-spots.
  \end{itemize}

  \begin{figure}
	  \begin{subfigure}{0.45\linewidth}
	  	\centering
	  	\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
	  	\caption{}
	  \end{subfigure}
	  \begin{subfigure}{0.45\linewidth}
	  	\centering
	  	\includegraphics[width=\linewidth]{rzplot_layered_280K_jet.png}
	  	\caption{}\label{fig:sandwiched280K}
	  \end{subfigure}
  \caption{R-spots increases in intensity when the temperature of the system is lowered to 280K.
  In this case, the simulated R-spots is more intense than experiment.}
  \end{figure}

  % %BJC3: update with 300K pics. Presented separately from 280K for now. 
%  \begin{figure}
%  \begin{subfigure}{0.3\linewidth}
%        \centering
%        \vspace{-0.2em}
%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_offset_300K.png}
%        \caption{}~\label{fig:rz_offset}
%  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%        \centering
%        \vspace{0.25em}
%        \includegraphics[scale=0.285]{WAXS_raw.png}
%        \caption{}~\label{fig:raw_waxs}
%  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%        \centering
%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_layered_300K.png}
%        \caption{}~\label{fig:rz_layered}
%  \end{subfigure}
%  \begin{subfigure}{0.0544\linewidth}
%        \centering
%        \vspace{-4.00em}
%        \includegraphics[width=\linewidth]{colorbar_seismic.png}
%  \end{subfigure}
%%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced. Any thoughts why? We can discuss in person.  And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
%%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
%%BJC2: Sure, I'll add that to supporting info
%%  \caption{The simulated XRD pattern generated from the equilibrated trajectory
%%	  of the parallel displaced configuration (a) exhibits all major reflections
%%	  present in the experimental WAXS pattern (b). The simulated XRD pattern
%%	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
%%	  all major reflections except R-double.}
%  \label{fig:XRDsim}
%  \end{figure}
